### 2024-09-23 manuscript.tex
ANN figure

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/ann.pdf}
\caption{
Artificial neural network (ANN) for prediction of precipitation in lidar
backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
\textbf{(b)} randomly selected example samples of near-surface backscatter in
four categories (clear, fog, rain and snow), as determined by coincident
human-performed weather observations, \textbf{(c)} receiver operating
characteristic diagram of the ANN, \textbf{(d)} examples of 10-day periods
human-observed (`HUM') and predicted precipitation based on an ANN trained on
all voyages (`ANN') and all voyages except for the shown voyage (`ANN2') during
three randomly selected voyages with the available data. Here, by `randomly
selected' we mean selected from the top of a permutation generated by a
pseudo-random number generator to prevent authors' bias in the selection.
}
\label{fig:ann}
\end{figure}
